Analytic Light Curves in Reflected Light: \\% Phase Curves, Occultations, and Non-Lambertian Scattering

### 2020-05-14 tex/ms.tex
added proof

\subsection{The integral along the terminator, $\tT$}
\label{sec:tT}
%
In this section we present a solution to Equation~(\ref{eq:tT}), the
line integral along the day/night terminator of the occulted body. As
before, the first thing we must do is derive expressions for the integration
limits $\pmb{\xi}$.
%
Depending on the integration case, these limits
will corresponds to the point of intersection between the terminator and
the limb of the occultor and/or the point of intersection between the
terminator and the limb of the occulted body. The former is given by
%
\begin{proof}{}
    \pmb{\xi_0} &=
    \atantwo\left(\sqrt{1 - {\mathbf{x''}}^2}, \mathbf{x''} \right)
\end{proof}
%
where $\mathbf{x''}$ are the roots of the quartic (Equation~\ref{eq:quartic}).
The latter is given by
%
\begin{proof}{}
    \xi_1 &=
    \begin{cases}
        0   & \qquad \qquad (1 - x_o'')^2 + {y_o''}^2 < r_o^2
        \\
        \pi & \qquad \qquad \text{otherwise}
        \quad.
    \end{cases}
\end{proof}
%
As before, these angles are then
wrapped to the range $[0, 2\pi)$ and
sorted into the vector
$\pmb{\xi}$ such that the integration is performed counter-clockwise
about the center of the integration region.
%
The middle panel of Figure~\ref{fig:geometry} shows a case where
$\xi_0 = 96.5^\circ$ corresponds to the point of intersection between the occultor
limb and the terminator and $\xi_1 = 0^\circ$ corresponds to the
point where the terminator extends onto the backside of the body.
%
Note, importantly, that unlike $\pmb{\phi}$, the angle $\pmb{\xi}$ is not
measured between the horizontal and a point on the curve of $\mathcal{T}$.
Recall that $\pmb{\xi}$ is an angular parameter of the ellipse, so it is
measured in the same way as the eccentric anomaly in a Keplerian orbit:
it is the
angle between the semi-major axis of the ellipse and the perpendicular
projection of a point on the ellipse onto the unit circle
(see Figure~\ref{fig:geometry}).

@@

of the binomial theorem. As before, we simply present the result, with
validation links:
\begin{proof}{}

@@

        -b\sin\theta'

@@

        Z^{0, l-2}_{0,k}

@@

        - \, \cos\theta'

@@

        -b\sin\theta'

@@

        \bigg(
        \sin\theta'

@@

        \qquad\qquad\qquad
        \, b\cos\theta'

@@

        \bigg)
        - \, \cos\theta'
        \bigg(
        \sin\theta'
        \mathrel{\raisebox{1.25em}{$\nu \, \text{odd}, \mu = 1, l \, \text{odd}$}}
        \qquad\qquad\qquad
        \, b\cos\theta'
        \bigg)

@@

@@

@@

\begin{proof}{}
\begin{proof}{}
        2 |b| b_c       & \qquad \pi < \xi \leq \frac{3\pi}{2}  \\
The components of the matrix $\viH$ are given by the integral

@@

This integral is the same as that in Equation (D27)

>>>>

\subsection{The integral along the terminator, $\tT$}
\label{sec:tT}
%
In this section we present a solution to Equation~(\ref{eq:tT}), the
line integral along the day/night terminator of the occulted body. As
before, the first thing we must do is derive expressions for the integration
limits $\pmb{\xi}$.
%
Depending on the integration case, these limits
will corresponds to the point of intersection between the terminator and
the limb of the occultor and/or the point of intersection between the
terminator and the limb of the occulted body. The former is given by
%
\begin{proof}{tT}
    \pmb{\xi_0} &=
    \atantwo\left(\sqrt{1 - {\mathbf{x''}}^2}, \mathbf{x''} \right)
\end{proof}
%
where $\mathbf{x''}$ are the roots of the quartic (Equation~\ref{eq:quartic}).
The latter is given by
%
\begin{proof}{tT}
    \xi_1 &=
    \begin{cases}
        0   & \qquad \qquad (1 - x_o'')^2 + {y_o''}^2 < r_o^2
        \\
        \pi & \qquad \qquad \text{otherwise}
        \quad.
    \end{cases}
\end{proof}
%
As before, these angles are then
wrapped to the range $[0, 2\pi)$ and
sorted into the vector
$\pmb{\xi}$ such that the integration is performed counter-clockwise
about the center of the integration region.
%
The middle panel of Figure~\ref{fig:geometry} shows a case where
$\xi_0 = 96.5^\circ$ corresponds to the point of intersection between the occultor
limb and the terminator and $\xi_1 = 0^\circ$ corresponds to the
point where the terminator extends onto the backside of the body.
%
Note, importantly, that unlike $\pmb{\phi}$, the angle $\pmb{\xi}$ is not
measured between the horizontal and a point on the curve of $\mathcal{T}$.
Recall that $\pmb{\xi}$ is an angular parameter of the ellipse, so it is
measured in the same way as the eccentric anomaly in a Keplerian orbit:
it is the
angle between the semi-major axis of the ellipse and the perpendicular
projection of a point on the ellipse onto the unit circle
(see Figure~\ref{fig:geometry}).

@@

of the binomial theorem. The result is given on the following
page in Equation~(\ref{eq:tn}) along with the usual validation link,
\begin{proof}{tT}
    \label{eq:Zuvjk}
    \intertext{and}
        2 |b| b_c       & \qquad \pi \leq \xi < \frac{3\pi}{2}  \\
\afterpage{
    \begin{proof}{tT}
        \label{eq:tn}
        \tag{\ref*{eq:Zuvjk}*}

@@

            -bb_c^3\sin\theta'

@@

            Z^{0, l-2}_{0,j}

@@

            - \, b_c^3\cos\theta'

@@

            -bb_c^3\sin^2\theta'

@@

            Z^{0, l-3}_{0,j}

@@

            - \, b b_c^3\cos^2\theta'
            Z^{0, l-3}_{0,j}
            \mathrel{\raisebox{0em}{$\nu \, \text{odd}, \mu = 1, l \, \text{odd}$}}
            - \, b_c^5\sin\theta'\cos\theta'

@@

@@

            bb_c^3\cos\theta'

@@

            - \, b_c^3\sin\theta'

@@

    \vfill
The solution to Equation~(\ref{eq:tn}) depends on the matrix
$\viH$, whose components are given by the integral

@@

The $\viH$ integral is the same as that in Equation (D27)
